First and foremost, I would like to thank my advisor, Professor Hari Sundaram, who has been the ideal role model in every way possible and a constant source of support on academic, personal, and many, many other matters. He has taught me what it means to be a researcher, from his curiosity and vision to his kindness, patience, and compassion. I sincerely admire his dedication to conducting insightful research with a real-world impact, and I will forever be grateful for all that he has done for me.

It is hard to put into words how thankful I am to Dr. Vikram Sharma Mailthody and Dr. Adit Krishnan, my friends and two of the most influential mentors in my time here at the University of Illinois. Vikram nurtured me from the very beginning and is still my go-to whenever I need advice. He taught me everything I needed to know to start my career in research (and otherwise), and without him, I would not have made it this far. Adit has been a fantastic collaborator, helping me face the many challenges of our work and ensuring that our work was as strong as possible. He has spent countless hours outside of his work, and I am incredibly fortunate to have someone so driven and intelligent working with me.

I want to thank Professor Wen-mei Hwu and Professor Jinjun Xiong at the IBM Center for Cognitive Computing Systems Research for all of their support and guidance while I was an undergraduate researcher in artificial intelligence. I would also like to thank my collaborators Professor Ewa Maslowska, Dr. Aravind Sankar, and the members of the Crowd Dynamics Lab for helping ground and shape my research ideas into promising directions with a real-world impact. I really enjoyed working with Dr. Hugo (Yu) Chen and Minxing Liu during my time at Meta/Facebook, and I want to thank them for their efforts and invaluable advice for my career.

I want to thank the Thomas and Stacey Siebel Foundation for supporting me with a Siebel Scholar Award and the Department of Computer Science Scholarship Committee for nominating me. This thesis was made possible with the Extreme Science and Engineering Discovery Environment (XSEDE) Expanse GPU cluster, which is supported by National Science Foundation grant number ACI1548562. This work was also generously supported by the National Center for Supercomputing Application’s Nano and Delta clusters.

I want to thank my family and friends who have supported me through this journey. A special shoutout to my academic twin, Nikash Walia, who has stuck with me throughout these four years. I am forever indebted to my parents, my sister, and Neha, for their unwavering love and support throughout my journey.